\vskip-0.6in Endogenous Politics and the Design of Trade Institutions

### 2016-08-25 to-do.tex
incorporate notes and streamline 'dynamic preferences' section

\section{``Dynamic preferences''}
	\begin{itemize}
		\item James: need to be more precise about when $\ga$ is evaluated
			\begin{itemize}
				\item Skeptical of comparative-static style result: can I really compare governments with different $\ga$'s?
			\end{itemize}
		\item References from Krishna and Sadowski (2014) ECTA
				\begin{itemize}
					\item Gul and Pesendorfer's (2001) Econometrica is a two-period model. No dynamic inconsistency; derive temptation and desire for commitment in a model with dynamically consistent preferences.
					\item Promising: Hammond, Peter J., ``Changing Tastes and Coherent Dynamic Choice,'' The Review of Economic Studies, Vol. 43, No. 1 (Feb., 1976)
					\item Even better, especially advertising example (credit Kyle): Becker, Gary. S. and George J. Stigler, ``De Gustibus Non Est Disputandum,'' The American Economic Review, Vol. 67, No. 2 (Mar., 1977), pp. 76-90
						\begin{itemize}
							\item I can make my argument almost exactly in analogy to this advertising example. My $\ga(e)$ function is like their $g(A)$.
						\end{itemize}
					\item Simpler: Becker, G. S. and K. M. Murphy (1993), “A Simple Theory of Advertising as a Good or Bad,” Quarterly Journal of Economics, 942-64.
				\end{itemize}
			\item At worst, I can use leg / exec split to deal with this criticism
			\item Mostafa, Nuno, Giovanni, Anson to some extent: Cardinal vs. ordinal
				\begin{itemize}
					\item Giovanni: if I can show properties survive  monotonic transformation, I'm fine
					\item They don't like gov't choosing its own preferences. May just need to change wording
				\end{itemize}
			\item Bob: what is fundamental structure of preferences?
			\item The way $e$ affects preferences doesn't change!!! Preferences are wrapped up in $\ga$!
			\item Devashish: Utility fcn didn't change. Just got evaluated at a different point
				\begin{itemize}
					\item Preferences don't change. It's persuasion that affects decision-making. 2nd story: Giovanni's ``expost $\ga(e)$ as effort to elect/choose ex-post decision-maker''
				\end{itemize}
		\end{itemize}
	Bob: maybe gov't has some other reason for setting non-zero tariff that opens the door for lobbies. 2nd best remedy for market failure, etc.

>>>>

\section{``Dynamic preferences''}
	\begin{itemize}

					\item Gul and Pesendorfer's (2001) Econometrica is a two-period model. No dynamic inconsistency; derive temptation and desire for commitment in a model with dynamically consistent preferences.
					\item Even better, especially advertising example (credit Kyle): Becker, Gary. S. and George J. Stigler, ``De Gustibus Non Est Disputandum,'' The American Economic Review, Vol. 67, No. 2 (Mar., 1977), pp. 76-90
					\item Simpler: Becker, G. S. and K. M. Murphy (1993), Simple Theory of Advertising as a Good or Bad, Quarterly Journal of Economics, 942-64.
						\begin{itemize}
							\item Their firms are my firm. Their consumers are my government
							\item Kyle's lit review talkes about `persuasive,' `informative,' and `complementary' views of advertisting. This is complementary.
							\item $e$ and $\tau$ enter objective function. Gov't is sophisticated, can make commitment that alters $e$ (i.e. behavior of another actor). But $CS + \ga(e)PS + \ldots$, just like $u(X,Y,A)$; says consumer could work to pass law about number of adds on TV each hour.
							\item Use newly drawn extensive form to explain this, lays out when welfare is realized
							\item Addresses James' concern about needing to be more precise about when $\ga$ is evaluated)
			\begin{itemize}
				\item Skeptical of comparative-static style result: can I really compare governments with different $\ga$'s?
			\end{itemize}

				\end{itemize}
			\item Mostafa, Nuno, Giovanni, Anson to some extent: Cardinal vs. ordinal
				\begin{itemize}
					\item Giovanni: if I can show properties survive  monotonic transformation, I'm fine
					\item They don't like gov't choosing its own preferences. May just need to change wording
				\end{itemize}
			\item Bob: what is fundamental structure of preferences?
			\item The way $e$ affects preferences doesn't change!!! Preferences are wrapped up in $\ga$!
			\item Devashish: Utility fcn didn't change. Just got evaluated at a different point
				\begin{itemize}
					\item Preferences don't change. It's persuasion that affects decision-making. 2nd story: Giovanni's ``expost $\ga(e)$ as effort to elect/choose ex-post decision-maker''
				\end{itemize}
		\end{itemize}
